### 2013-04-10 MSteenhagen-CV.tex
Teaching experience; moved RA to back
Moved professional organisations to back

\marginhead{Appointments}

@@

\ind 2009--Present. Research Assistant in Philosophy, working on philosophy of psychology, clinical methodology and psychoanalysis.

@@

\ind 2012. ``Imaginary Experience.'' University of Warwick, London-Warwick Graduate Mind Forum.

@@

\ind 2012. ``Researching the Self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.

@@

\ind 2011. ``Representing the Trinity.'' University of Ghent, NGE Annual conference .

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip
\marginhead{Professional organisations}

@@

@@

>>>>

\marginhead{Teaching experience}

@@

@@

\ind 2012. ``Imaginary experience.'' University of Warwick, London-Warwick Graduate Mind Forum.

@@

\ind 2012. ``Researching the self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.

@@

\ind 2011. ``Representing the trinity.'' University of Ghent, NGE Annual conference .

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip

@@

\ind 2009--Present. Research Assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.

@@

\marginhead{Professional organisations}
